A Generalized Sphere Theorem for Positively Curved Combinatorial 3-Manifolds

### 2013-04-15 paper/paper.tex
more writing, messing with figures, more to-dos

\noindent The proof of this theorem relies on the remarkable work of Lutz, Sullivan and Sulanke in \cite{Lutz07, LutzSul_unpub, sulanke2009isomorphism} who created a complete census of positively curved combinatorial 3-manifolds (see \cite{Lutz_online}.) This census contains 4787 manifolds, with the following topologies represented: the 3-sphere $S^3$, the real projective space $\mathbb{RP}^3$, the lens spaces $L(3,1)$ and $L(4,1)$, and the cube space $S^3/Q$. Note that all manifolds are either homeomorphic to a 3-sphere or to the quotient space of a 3-sphere under the action of a finite group.

Here is a table of the number of triangulations in the census at each topological type and diameter.\vspace{.1in}

\begin{tabular} {| l l | l l | l l | l l | l l |}
\hline
\multicolumn{2}{|c|}{$S^{3}/Q$} &
\multicolumn{2}{|c|}{$L(3,1)$} &
\multicolumn{2}{|c|}{$RP^{3}$} &
\multicolumn{2}{|c|}{$S^{3}$} &
\multicolumn{2}{|c|}{$L(4,1)$} \\
\hline
\hline
$1H$&1    &$2E$&1    &$1H$&10    &$1E$&3    &$1J$&1 \\
  &       &$1J$&1    &$2E$&7     &$1H$&173  &    &  \\
  &       &  &       &$1J$&5     &$2E$&401  &    &  \\
  &       &  &       &    &      &$1J$&2438 &    &  \\
  &       &  &       &    &      &$3E$&1060 &    &  \\
  &       &  &       &    &      &$2H$&582  &    &  \\
  &       &  &       &    &      &$4E$&93   &    &  \\
  &       &  &       &    &      &$2J$&11   &    &  \\
\hline
\end{tabular}\vspace{.1in}

\noindent Here is a table of the number of triangulations at each diameter. \vspace{.1in}

@@

\begin{figure}
    \begin{center}
    \includegraphics[width=0.6\linewidth]{figures/global_statistics.png}
    \caption{Global statistics. TO DO: Change diameter labels to $1, H, 2, J, 3, 2H, 4, 2J$ and put these on horizontal axis. TO DO: Change graph to show separate data points for each topological type. }
    \end{center}
    \label{global_statistics}
\end{figure}

>>>>

\noindent The proof of this theorem relies on the remarkable work of Lutz, Sullivan and Sulanke in \cite{Lutz07, LutzSul_unpub, sulanke2009isomorphism} who created a complete census of positively curved combinatorial 3-manifolds along with a list of their topological types, see \cite{Lutz_online_manifolds} and \cite{Lutz_online_topological_types}. This census contains 4787 manifolds, with the following topologies represented: the 3-sphere $S^3$, the real projective space $\mathbb{RP}^3$, the lens spaces $L(3,1)$ and $L(4,1)$, and the cube space $S^3/Q$. Note that all manifolds are either homeomorphic to a 3-sphere or to the quotient space of a 3-sphere under the action of a finite group.

Here is a table of the number of triangulations in the census at each topological type and diameter. TO DO: CHANGE ORDER OF MANIFOLDS IN TABLE TO S3/Q, L(4,1), L(3,1), RP3, S3. TO DO: PUT EACH POSSIBLE DIAMETER IN TABLE ON ITS OWN COLUMN (TO ALIGN THEM WITH LABELS ON THE LEFT...) \vspace{.1in}

\begin{tabular} {| l l | l l | l l | l l | l l |}
\hline
\multicolumn{2}{|c|}{$S^{3}/Q$} &
\multicolumn{2}{|c|}{$L(3,1)$} &
\multicolumn{2}{|c|}{$RP^{3}$} &
\multicolumn{2}{|c|}{$S^{3}$} &
\multicolumn{2}{|c|}{$L(4,1)$} \\
\hline
\hline
$1H$&1    &$2E$&1    &$1H$&10    &$1E$&3    &$1J$&1 \\
  &       &$1J$&1    &$2E$&7     &$1H$&173  &    &  \\
  &       &  &       &$1J$&5     &$2E$&401  &    &  \\
  &       &  &       &    &      &$1J$&2438 &    &  \\
  &       &  &       &    &      &$3E$&1060 &    &  \\
  &       &  &       &    &      &$2H$&582  &    &  \\
  &       &  &       &    &      &$4E$&93   &    &  \\
  &       &  &       &    &      &$2J$&11   &    &  \\
\hline
\end{tabular}

\noindent Here is a table of the number of triangulations at each diameter. TO DO: MAKE THIS A "TOTAL" COLUMN IN PREVIOUS TABLE.\vspace{.1in}

@@

\begin{figure}
    \begin{center}
    \includegraphics[width=0.9\linewidth]{figures/global_statistics.png}
    \caption{Global statistics. TO DO: Change diameter labels to $1, H, 2, J, 3, 2H, 4, 2J$ and put these on horizontal axis. TO DO: Change graph to show separate data points for each topological type. }
    \end{center}
    \label{global_statistics}
\end{figure}
